\documentclass[oneside,10pt]{article}

% fonts
\usepackage[psamsfonts]{amsfonts}
\usepackage[psamsfonts]{amssymb}
\usepackage{amsmath}
\usepackage{txfonts}

% hyphenation rules for Dutch

\usepackage[dutch,english]{babel}
\usepackage[sc,osf]{mathpazo}
\usepackage[force]{textcomp}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MARGINS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% to get the layout right
\usepackage[top=1.5in, bottom=1in, left=1in, right=1in]{geometry}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\selectlanguage{english}
\pagestyle{empty}
{
\centering

{\LARGE Propositions \\}
\vspace{0.5cm}
{\large pertaining to the thesis \\}
\vspace{0.5cm}
{\LARGE Planetary-scale surface water detection from space \\ }
\vspace{0.5cm}
{\large Gennadii Donchyts, Month DD, 2017 \\}
}

%\vfill

{
%\large
\newcommand{\citat}[1]{\smth \hfill {\small #1}}
\newcommand{\smth}{$\left.\right.$}


\begin{enumerate}

\item Globally applicable, locally accurate and efficient surface water change detection methods are easier to implement than it was thought.
\citat{this thesis}

\item Aral Sea and Tibetan Plateau are the largest contributors to global surface water changes over the last three decades. \\
% coastline lengths infinite ... vs area 
% 30m, <30m 
\citat{this thesis}

\item A combination of discriminative and generative methods provide better results when compared to only discriminative methods of surface water detection from EO data. \\
% te saai, slap
\citat{this thesis}

%\item Combining EO data with VGI provides more value when compared to the use of one of these types of data separately. \\
%\citat{this thesis}

\item We can build dikes and reclaim land faster when compared to the land claimed by the rising seas. \\
\citat{this thesis}

\item Tractability and scalability are more important than accuracy and correctness. \\

\item By moving all EO data and its processing to the Cloud we significantly reduce its explorability. \\

\item In a few years, many EO scientists will have to learn how to process videos to do their research. \\

\item With the annual growth in online data of zettabytes per year, Artificial Intelligence, Machine Learning, and Deep Learning are becoming indispensable tools to gain new value from historical measurement data.

\item The singularity is near.

% \item Five hour a week learning rule is a necessity to survive in the modern world.

% \item Online education is changing the world.

\item Perfection is a subjective illusion.

\end{enumerate}
}

\vspace{0.5cm}
\noindent These propositions are regarded as opposable and defendable, and have been approved as such by the promotor, Prof.~dr. Nick van de Giesen.

\end{document}
