\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}

\setheader{List of Publications}
\label{publications}

\subsection*{List of Journal Publications}

%% We use the 'etaremune' environment (the reverse of 'enumerate') to get a
%% numbered list of publications in reverse chronological order. If the list of
%% authors is long, it might be useful to emphasize your own name with \textbf.
\begin{etaremune}{\small

\item \textbf{Donchyts, G.}, Schellekens, J., Winsemius, H., Eisemann, E., van de Giesen, N. (2016). A 30 m Resolution Surface Water Mask Including Estimation of Positional and Thematic Differences Using Landsat 8, SRTM and OpenStreetMap: A Case Study in the Murray-Darling Basin, Australia. Remote Sensing, 8(5), 386.

\item \textbf{Donchyts, G.}, Baart, F., Winsemius, H., Gorelick, N., Kwadijk, J., van de Giesen, N. (2016). Earth's surface water change over the past 30 years. Nature Climate Change, 6(9), 810-813.

\item Luijendijk, A., Hagenaars, G., Baart, F., \textbf{Donchyts, G.}, Aarninkhof, S., Ranasinghe, F. (2017). Global sandy shorelines changes derived from satellite images, Nature (submitted)

% \item TODO: submit \textbf{Donchyts, G.}, Gorelick, N., Winsemius, H., Schellekens, J., van de Giesen, N. (2017). Reconstruction of reservoir and lake surface area dynamics from optical and SAR satellite imagery, Journal of Remote Sensing (in preparation)

% Rapid setup of hydrological and hydraulic models using OpenStreetMap and the SRTM derived digital elevation model

}\end{etaremune}


\subsection*{List of Conferences}

%% We use the 'etaremune' environment (the reverse of 'enumerate') to get a
%% numbered list of publications in reverse chronological order. If the list of
%% authors is long, it might be useful to emphasize your own name with \textbf.
\begin{etaremune}{\small

\item \textbf{Donchyts, G.}, van de Giesen, N., Gorelick, N. (2017). Reconstruction of reservoir and lake surface area dynamics from optical and SAR satellite imagery. 9th International Workshop on the Analysis of Multitemporal Remote Sensing Images (MultiTemp), Bruges, Belgium.

\item \textbf{Donchyts, G.}, Baart, F., Gorelick, N., Eisemann, E., van de Giesen, N. (2017). Fast segmentation of satellite images using SLIC, WebGL and Google Earth Engine. EGU General Assembly Conference Abstracts, 19, p.18283.

\item \textbf{Donchyts, G.},  Winsemius, H.C.; Schellekens, J.; Erickson, T.; Gao, H.; Savenije, H.; van de Giesen, N. (2016). Global 30m Height Above the Nearest Drainage. EGU General Assembly Conference Abstracts, 18 p.17445.

\item \textbf{Donchyts, G.},  Winsemius, H.C.; Schellekens, J.; Erickson, T.; Gao, H.; Savenije, H.; van de Giesen, N. (2016). Global 30m Height Above the Nearest Drainage. EGU General Assembly Conference Abstracts, p.17445.

\item \textbf{Donchyts, G.},  Jagers, B.; van de Giesen, N.; Baart, F.; van Dam, A. (2015). Automated estimation of river bathymetry using change detection based on Landsat imagery and river morphological models. Proceedings of the AGU fall meeting.

\item \textbf{Donchyts, G.},  Schellekens, J.; Winsemius, H.C.; van de Giesen, N. (2015). Quality assessment of OpenStreetMap water mask using LANDSAT 8 imagery and Google Earth Engine. EGU General Assembly Conference Abstracts, 17, p.12021.

}\end{etaremune}


% http://metis.tudelft.nl:7777/pls/metis_lookup/pk_apa_n.results?p_url_id=5403&p_onderzoekernummer=1104023