\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\label{acknowledgements}

\dropcap{T}his journey would be impossible without the support of my family, professors and mentors, and friends. 

I would like to thank Delft University of Technology, Deltares, the FP7 European Commission project earth2Observe, and the SERVIR-Mekong project for funding the research presented in this thesis. I would like to express my most profound gratitude to my supervisors Nick van de Giesen, Elmar Eiseman and Bert Jagers for guiding me throughout this research project. Nick, I could not have imagined having a better advisor and mentor for my Ph.D. study. I am grateful to my colleagues Hessel Winsemius, Jaap Schellekens, Fedor Baart, Jaap Kwadijk, Joost Icke, Gerard van de Kolff, Arthur Baart for their patience and support in overcoming numerous obstacles I have been facing through my research. I am also grateful to Google for providing Cloud Compute Services credits which helped me to get results faster and of a better quality. Working with the Google Earth Engine community and software engineers was a great pleasure. Noel Gorelick, Nicolas Clinton, Tyler Ericson, Simon Ilyushchenko, Matt Hancher, George Azzari, Guido Lemoine, Sam Murphy and many other active participants of the Google Earth Engine Developers Forum - I've learned a lot from you during sleepless nights while working on this research. I would like to express my special gratitude to Dr. Mark Zheleznyak who gave the start to my scientific career in Ukraine. To my wife Olga Donchyts and son Daniel Alexandr Donchyts, thank you for supporting and inspiring me in all of my pursuits.
